A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-08 method.tex
Reverting 606
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@607 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{I didn't mention the upsampling and downsampling overhead, but I included it in my calculation.  Should I describe this here, in an appendix, or in a publicly available tech note in the \textsc{dcc}?} An example time slice design satisfying these constraints for a $1.4 - 1.4 \, M_{\odot}$ is shown in table~\ref{table:time_slices} below.  For this example, the latency for this time slice design is just
%
%$\input{time_slice_latency.tex}$
%
even if all of the time slices are implemented with the \textsc{fft} method.  This set of time slices will require
%
%$\input{time_slice_ops_firslice.tex}$ operations per sample per template, compared with $\input{time_slice_ops_conv.tex}$
%
for pure \textsc{fft} cross-correlation without time slices, or
%
%$\input{time_slice_ops_td.tex}$
%
for the \textsc{fir} filter method without time slices.

\begin{table}[!h]
\caption{Example of critically sampled, power-of-2 time slices for a $1.4 - 1.4 \, M_{\odot}$ template extending from $f_\mathrm{low} = 10 \, \mathrm{Hz}$ to $f_\mathrm{ISCO} = 1571\, \mathrm{Hz}$ with a time frequency structure given by ($\ref{eq:fgw})$.}
\label{table:time_slices}
\begin{minipage}[c]{0.5\textwidth}
\centering
%\includegraphics[trim = 3cm 0cm 1.5cm 0cm, scale=0.4]{time_slices.pdf}
\end{minipage}
\begin{minipage}[c]{0.3\textwidth}
\centering
%\input{time_slices.tex}
\end{minipage}
\end{table}

>>>>

\editorial{I didn't mention the upsampling and downsampling overhead, but I included it in my calculation.  Should I describe this here, in an appendix, or in a publicly available tech note in the \textsc{dcc}?} An example time slice design satisfying these constraints for a $1.4 - 1.4 \, M_{\odot}$ is shown in table~\ref{table:time_slices} below.  For this example, the latency for this time slice design is just $\input{time_slice_latency.tex}$ even if all of the time slices are implemented with the \textsc{fft} method.  This set of time slices will require $\input{time_slice_ops_firslice.tex}$ operations per sample per template, compared with $\input{time_slice_ops_conv.tex}$ for pure \textsc{fft} cross-correlation without time slices, or $\input{time_slice_ops_td.tex}$ for the \textsc{fir} filter method without time slices.

\begin{table}[!h]
\caption{Example of critically sampled, power-of-2 time slices for a $1.4 - 1.4 \, M_{\odot}$ template extending from $f_\mathrm{low} = 10 \, \mathrm{Hz}$ to $f_\mathrm{ISCO} = 1571\, \mathrm{Hz}$ with a time frequency structure given by ($\ref{eq:fgw})$.}
\label{table:time_slices}
\begin{minipage}[c]{0.5\textwidth}
\centering
\includegraphics[trim = 3cm 0cm 1.5cm 0cm, scale=0.4]{time_slices.pdf}
\end{minipage}
\begin{minipage}[c]{0.3\textwidth}
\centering
\input{time_slices.tex}
\end{minipage}
\end{table}
